A Multi-Modal Model for Prediction and Classification of Object Deformation during Robotic Manipulation

### 2016-08-26 twostagedo.tex
Temp

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A} major challenge in robotic manipulation is to plan actions with objects so as to deform them into new shapes. Most objects that are manipulated by animals in natural environments are deformable, including objects that are elastic, plastic, breakable, tearable, and spreadable. \comment{The work reported here is based on the premise that in order to plan manipulations of deformable objects, the sensorimotor contingencies governing object deformation are required. A sensorimotor contingency is simply defined as the relationship between the robot's actions and the resultant changes in its observations. Thus different materials (elastic, plastic) present have different sensorimotor contingencies. The main hypothesis is that predictive models of these sensorimotor contingencies can be learned from data. These learned models can then be used to make the predictions required for planning. The predictions of a learned model can be fed back into the model, to predict an object's deformation behaviour over a variety of time scales. Without such predictions planners cannot reason about the effects of actions, or sequences of actions, to achieve desired effects.

Various models of deformation are used in engineering, such as finite element models, but these typically require careful optimisation by hand, and cannot run in real time. In graphics there are many methods used for generating qualitatively plausible simulations of deformable objects, but these are not easy to fit to real data. In contrast, robots must learn model parameters from data, on-line, in reasonable amounts of training time. This includes learning from the limited sensing typically available, such as partial visual views of an object, and force-torque monitoring only at contact points. Thus, tackling the prediction problem in robotics adds additional difficulties to an already challenging problem.}

@@

The contour of the deformable object is used to obtain the ground truth for the training phase, which is the area enclosed by the contour. Geometrically, the contour is represented by a polygon with hundreds of sides, which can also be called a \textit{linear spline}.  The tracking of the deformable target in the ground truth has two stages:
\begin{enumerate}
 \item The target object is segmented from the environment.  The Canny algorithm is used to extract the edges of the image.  Next, a simple colour segmentation is used to remove edges that are not likely to belong to the object of interest.
 \item The internal representation of its contour, the linear snake, is adapted to its new shape.  The algorithm assumes that no occlusions take place and that the contour does not bend over itself.
\end{enumerate}
For the first frame, the snake is initialised as a rectangle around the target. This rectangle fragments itself into smaller pieces. Each new vertex adheres itself to the closest point on an edge, as reached by growing rings of pixels around its current position, up to a certain threshold distance [\fref{fig:scene}(a)].  If there is no edge within that area, the control point remains were it is. This criterion was selected to make the representation more robust against edges that are easier to detect on some frames than in others.  Once the edge reappears, the control point adapts itself again.  Also, the distance between two consecutive control points is kept within the interval $[min\_distance, max\_distance]$ and two adjacent edges do not form angles smaller than $min\_angle$.  See \alref{alg:regularise}.  This allows the snake to adapt very quickly to the complexity of the contour it represents.

@@

\begin{figure}
  \begin{algorithmicieee}{Evolutionary Search}\label{alg:genetic}
 \STATE Be $N$ the number of sets of parameters to be evaluated per generation and $M$ the number of generations to try.
 \STATE Let $\alpha + \beta + \gamma + \zeta = N$ denote four portions of the $N$ elements.
 \STATE Be $\sigma_{max} > \sigma_{min}$ standard deviations for a Gaussian
 \STATE Let $\Delta\sigma \gets (\sigma_{max} - \sigma_{min})/M$.
 \FOR {$i=1 \to M$}
 \STATE Run the $N$ simulations and compare prediction with the ground truth (real object), by comparing the area occupied by the real object with the area occupied by the mesh of the simulation [\fref{fig:scene}(b)].
 \STATE Keep the best $\alpha$ of all simulations.
 \STATE $\sigma \gets \sigma - \Delta\sigma$
 \STATE Generate $\beta$ by adding random Gaussian noise, with standard deviation $\sigma$, to the best candidates.
 \STATE Generate $\gamma$ by selecting values of the parameters from two different sets at random, after eliminating the $\epsilon$ worst.
 \FOR {$\zeta$ elements}
   \STATE Generate completely new sample with:
   \FOR {every parameter}
     \STATE $n \leftarrow randomNumber \in [0,1)$
     \STATE $min \leftarrow \log(minValue)$
     \STATE $max \leftarrow \log(maxValue)$
     \STATE $param \leftarrow e^{(n (max - min) + min)}$
   \ENDFOR
 \ENDFOR
 \STATE $i \gets i + 1$
 \ENDFOR
\end{algorithmicieee}
 \caption{Evolutionary Search for Automatic Calibration}
\end{figure}

>>>>

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A} major challenge in robotic manipulation is to plan actions with objects so as to deform them into new shapes. Most objects that are manipulated by animals in natural environments are deformable, including objects that are elastic, plastic, breakable, tearable, and spreadable. \comment{The work reported here is based on the premise that in order to plan manipulations of deformable objects, the sensorimotor contingencies governing object deformation are required. A sensorimotor contingency is simply defined as the relationship between the robot's actions and the resultant changes in its observations. Thus different materials (elastic, plastic) present have different sensorimotor contingencies. The main hypothesis is that predictive models of these sensorimotor contingencies can be learned from data. These learned models can then be used to make the predictions required for planning. The predictions of a learned model can be fed back into the model, to predict an object's deformation behaviour over a variety of time scales. Without such predictions planners cannot reason about the effects of actions, or sequences of actions, to achieve desired effects.}

\comment{Various models of deformation are used in engineering, such as finite element models, but these typically require careful optimisation by hand, and cannot run in real time. In graphics there are many methods used for generating qualitatively plausible simulations of deformable objects, but these are not easy to fit to real data. In contrast, robots must learn model parameters from data, on-line, in reasonable amounts of training time. This includes learning from the limited sensing typically available, such as partial visual views of an object, and force-torque monitoring only at contact points. Thus, tackling the prediction problem in robotics adds additional difficulties to an already challenging problem.}

@@

The contour of the deformable object is used to obtain the ground truth for the training phase, which is the area enclosed by the contour. Geometrically, the contour is represented by a polygon with hundreds of sides, which can also be called a \textit{linear spline}.  The tracking of the deformable target in the ground truth has two stages:
\begin{enumerate}
 \item The target object is segmented from the environment.  The Canny algorithm is used to extract the edges of the image.  \comment{\sout{Next, a simple colour segmentation is used to remove edges that are not likely to belong to the object of interest.}  Since the object of interest has an outstanding colour, the hue of the pixels on every edge }
 \item The internal representation of its contour, the linear snake, is adapted to its new shape.  The algorithm assumes that no occlusions take place and that the contour does not bend over itself.
\end{enumerate}
For the first frame, the snake is initialised as a rectangle around the target. This rectangle fragments itself into smaller pieces. Each new vertex adheres itself to the closest point on an edge, as reached by growing rings of pixels around its current position, up to a certain threshold distance [\fref{fig:scene}(a)].  If there is no edge within that area, the control point remains were it is. This criterion was selected to make the representation more robust against edges that are easier to detect on some frames than in others.  Once the edge reappears, the control point adapts itself again.  Also, the distance between two consecutive control points is kept within the interval $[min\_distance, max\_distance]$ and two adjacent edges do not form angles smaller than $min\_angle$.  See \alref{alg:regularise}.  This allows the snake to adapt very quickly to the complexity of the contour it represents.

@@

\begin{figure}
  \begin{algorithmicieee}{Evolutionary Search}\label{alg:genetic}
 \STATE Be $N$ the number of sets of parameters to be evaluated per generation and $M$ the number of generations to try.
 \STATE Let $\alpha + \beta + \gamma + \zeta = N$ denote four portions of the $N$ elements\comment{, with: \\
 $\alpha \leftarrow$ number of elements that survive for the next generation as they are, \\
 $\beta \leftarrow$ mutated individuals, \\
 $\gamma \leftarrow$ crossed over, and \\
 $\zeta \leftarrow$ new individuals. \\
 which will be chosen as follows:}
 \STATE Be $\sigma_{max} > \sigma_{min}$ standard deviations for a Gaussian
 \STATE Let $\Delta\sigma \gets (\sigma_{max} - \sigma_{min})/M$.
 \FOR {$i=1 \to M$}
 \STATE Run the $N$ simulations and compare prediction with the ground truth (real object), by comparing the area occupied by the real object with the area occupied by the mesh of the simulation [\fref{fig:scene}(b)].
 \STATE Keep the best $\alpha$ of all simulations.
 \STATE $\sigma \gets \sigma - \Delta\sigma$
 \STATE Generate $\beta$ by adding random Gaussian noise, with standard deviation $\sigma$, to the best candidates.
 \STATE Generate $\gamma$ by selecting values of the parameters from two different sets at random, after eliminating the $\epsilon$ worst.
 \FOR {$\zeta$ elements}
   \STATE Generate completely new sample with:
   \FOR {every parameter}
     \STATE $n \leftarrow randomNumber \in [0,1)$
     \STATE $min \leftarrow \log(minValue)$
     \STATE $max \leftarrow \log(maxValue)$
     \STATE $param \leftarrow e^{(n (max - min) + min)}$
   \ENDFOR
 \ENDFOR
 \STATE $i \gets i + 1$
 \ENDFOR
\end{algorithmicieee}
 \caption{Evolutionary Search for Automatic Calibration}
\end{figure}
